\texttt{SuperScreen}: An open-source package for simulating the magnetic response of 2D superconductors

### 2021-08-02 main_cpc.tex
Updates from Overleaf

def make_ring(
    inner_radius=2.5,
    outer_radius=5,
    Lambda=1,
    length_units="um",
    square=False,
):
    if square:
        name = "square_ring"
        outer_points = sc.geometry.square(
            outer_radius * 2, points_per_side=60
        )
        inner_points = sc.geometry.square(
            inner_radius * 2, points_per_side=20
        )
        bbox_points = sc.geometry.square(
            outer_radius * 2 * 1.4, points_per_side=5
        )
    else:
        name = "circular_ring"
        outer_points = sc.geometry.circle(outer_radius)
        inner_points = sc.geometry.circle(inner_radius)
        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=2)

@@

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/ring_mesh.png}
  \caption{A subfigure}
  \label{fig:circular_ring_mesh}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/ring_mesh.png}
  \caption{A subfigure}
  \label{fig:square_ring_mesh}
\end{subfigure}
\caption{A figure with two subfigures}
\label{fig:ring_mesh}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.40]{examples/images/ring/ring_uniform_field.png}
    \caption{Caption}
    \label{fig:ring_uniform_field}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.40]{examples/images/ring/ring_circulating_current.png}
    \caption{Caption}
    \label{fig:ring_circ_current}
\end{figure}

>>>>

def make_ring(
    inner_radius=2.5,
    outer_radius=5,
    Lambda=1,
    length_units="um",
    square=False,
):
    if square:
        name = "square_ring"
        outer_points = sc.geometry.square(
            outer_radius * 2, points_per_side=60
        )
        inner_points = sc.geometry.square(
            inner_radius * 2, points_per_side=20
        )
        bbox_points = sc.geometry.square(
            outer_radius * 2 * 1.4, points_per_side=5
        )
    else:
        name = "circular_ring"
        outer_points = sc.geometry.circle(outer_radius)
        inner_points = sc.geometry.circle(inner_radius)
        bbox_points = sc.geometry.circle(outer_radius * 1.4, points=21)

@@

\begin{figure}
\centering
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
  \caption{A subfigure}
  \label{fig:circular_ring_mesh}
\end{subfigure}%
\begin{subfigure}{.45\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
  \caption{A subfigure}
  \label{fig:square_ring_mesh}
\end{subfigure}
\caption{A figure with two subfigures}
\label{fig:ring_mesh}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.40]{examples/images/ring/circular_ring_uniform_field.png}
    \caption{Caption}
    \label{fig:ring_uniform_field}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=.40]{examples/images/ring/circular_ring_circulating_current.png}
    \caption{Caption}
    \label{fig:ring_circ_current}
\end{figure}
